Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-03 aggexplain/introduction.tex
some summaries

Using the interpretable model and human expert knowledge, it was possible to detect this systematic bias in the data before deploying the model.
However, using interpretable machine learning algorithms typically penalizes their capacity, thus lowering the potential accuracy of the model \cite{Caruana:2015:IMH:2783258.2788613} or is only superficially more interpretable by being interpretable on a small scale but not for more complex tasks (\cite{2016arXiv160603490L,2016arXiv160605685K}).
As a way to interpret the behavior of machine learning models \emph{independently} from the used algorithm, black-box and more precisely, instance-level explanations recently became popular \cite{Martens:2014:EDD:2600518.2600523,DBLP:journals/corr/RibeiroSG16,krause2016interacting}.

>>>>

Using the interpretable model and human expert knowledge, it was possible to detect this systematic bias in the data before deploying the model.
However, using interpretable machine learning algorithms typically penalizes their capacity, thus lowering the potential accuracy of the model \cite{Caruana:2015:IMH:2783258.2788613} or is only superficially more interpretable by being interpretable on a small scale but not for more complex tasks (\cite{lipton2016mythos,2016arXiv160605685K}).
As a way to interpret the behavior of machine learning models \emph{independently} from the used algorithm, black-box and more precisely, instance-level explanations recently became popular \cite{Martens:2014:EDD:2600518.2600523,DBLP:journals/corr/RibeiroSG16,prospector}.

### 2018-04-03 explainer/abstract.tex
clean-up of machine learning
bug fixes
fix figures and some citations
some summaries

>>>>

\begin{contributions}{\todo{How can the model building}}
\item \todo{that it is not only possible to understand decision making of a predictive model through the model diagnostic workflow based on aggregated instance level explanations, but also how it can be applied for semantic validation and feature engineering on the input data.}
\item \todo{TODO}
\end{contributions}

### 2018-04-03 infuse/abstract.tex
fix figures and some citations
some summaries

>>>>

\begin{contributions}{How do different feature selection strategies compare to each other?}
\item Different strategies prefer different, equally reasonable, feature sets without having a significant impact on predictive performance.
\item Inspecting and comparing alternate settings lets machine learning experts develop insights that overwrite their initial intuitions.
\item Rankings from feature selection strategies are not informative enough to help understand model decisions.
\end{contributions}

### 2018-04-03 prospector/related_work.tex
some summaries

Having access to the internals of a machine learning algorithm also allows direct interaction with the models and to improve them on the fly.
BaobabView (van den Elzen and van Wijk~\cite{6102453}) offers interactive decision tree construction.
Steed~\etal~\cite{5332586,doi:10.1559/152304009788988314}
guides regression model creation by enhancing interaction
with the input data.
EnsembleMatrix (Talbot~\etal~\cite{Talbot:2009:EIV:1518701.1518895})
allows users to combine already computed classification models to
build ensemble models.
Some recent interactive machine learning tools \cite{
amershi15,
Amershi:2011:DEE:2046396.2046416,
Amershi:2012:RIM:2207676.2207680,
Amershi:2011:CHF:1978942.1978966,
Kapoor:2010:IOS:1753326.1753529,
kim2015scalable,
Leung2014710,
Mishra:2015:SAI:2700171.2791022,
export:141330})
are more algorithm agnostic, but depend on general
performance measures like confusion matrices,
area under ROC curve (AUC) measures,
result distribution of data points, and
feature weights according to model independent statistics.

>>>>

Having access to the internals of a machine learning algorithm also allows direct interaction with the models and to improve them on the fly.
BaobabView (van den Elzen and van Wijk~\cite{van2011baobabview}) offers interactive decision tree construction.
Steed~\etal~\cite{steed2009guided,steed2009tropical}
guides regression model creation by enhancing interaction
with the input data.
EnsembleMatrix (Talbot~\etal~\cite{Talbot:2009:EIV:1518701.1518895})
allows users to combine already computed classification models to
build ensemble models.
Some recent interactive machine learning tools \cite{
amershi15,
Amershi:2011:DEE:2046396.2046416,
Amershi:2012:RIM:2207676.2207680,
Amershi:2011:CHF:1978942.1978966,
Kapoor:2010:IOS:1753326.1753529,
kim2015scalable,
Leung2014710,
Mishra:2015:SAI:2700171.2791022,
export:141330})
are more algorithm agnostic, but depend on general
performance measures like confusion matrices,
area under ROC curve (AUC) measures,
result distribution of data points, and
feature weights according to model independent statistics.
